Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-03-21 article.rnw
Change \aicnum to \icnum to reflect that it may now be a different information criterion.

\newcommand\rsquarednum[1]{\num[round-mode=places,round-precision=3]{#1}}
\newcommand\aicnum[1]{\num{#1}}
\newcommand\probnum[1]{\num[round-mode=places,round-precision=3]{#1}}
\newcommand\cornum[1]{\num[round-mode=places,round-precision=3]{#1}}

@@

The $R^2$ values of the models ranged from \rsquarednum{\Sexpr{min(brute_data$statistics$R2)}} to \rsquarednum{\Sexpr{max(brute_data$statistics$R2)}}.
The AIC values ranged from \aicnum{\Sexpr{min(brute_data$statistics[[ic]])}} to \aicnum{\Sexpr{max(brute_data$statistics[[ic]])}}.
The ungrouped model gave an AIC value of \aicnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}.
\Cref{fig:aic} shows the distribution of AIC values from the models, with some models of interest marked.

@@

	\caption{%
		A histogram of the AIC values of species interaction models with all possible groupings of interaction coefficients.
		The green line shows the AIC value (\aicnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}) of the ungrouped model, in which all competition coefficients are fitted independently.
		The red line shows the AIC value (\aicnum{\Sexpr{brute_data$fully_grouped_statistics[[ic]]}}) of the fully grouped model, where every pair of species shares a single interaction coefficient.
	}
	\label{fig:aic}
\end{figure}

@@

Considering only models in which the rows and columns were grouped using the same grouping, the AIC values ranged from \aicnum{\Sexpr{min(brute_data$equivalently_grouped_statistics[[ic]])}} to \aicnum{\Sexpr{max(brute_data$equivalently_grouped_statistics[[ic]])}}; neither the best nor worst overall models had equivalently grouped rows and columns.
The total Akaike weight assigned to these models was \probnum{\Sexpr{brute_data$equivalently_grouped_weight}}; more than expected by chance (\probnum{\Sexpr{brute_data$equivalently_grouped_expected_weight}}), but not significantly so (Monte Carlo permutation test, $p=\probnum{\Sexpr{brute_data$equivalently_grouped_weight_p #$}}$).
This indicates that the most parsimonious model is not especially likely to be one that groups the rows and columns equivalently.

>>>>

\newcommand\rsquarednum[1]{\num[round-mode=places,round-precision=3]{#1}}
\newcommand\icnum[1]{\num{#1}} %For information criteria.
\newcommand\probnum[1]{\num[round-mode=places,round-precision=3]{#1}}
\newcommand\cornum[1]{\num[round-mode=places,round-precision=3]{#1}}

@@

The $R^2$ values of the models ranged from \rsquarednum{\Sexpr{min(brute_data$statistics$R2)}} to \rsquarednum{\Sexpr{max(brute_data$statistics$R2)}}.
The AIC values ranged from \icnum{\Sexpr{min(brute_data$statistics[[ic]])}} to \icnum{\Sexpr{max(brute_data$statistics[[ic]])}}.
The ungrouped model gave an AIC value of \icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}.
\Cref{fig:aic} shows the distribution of AIC values from the models, with some models of interest marked.

@@

	\caption{%
		A histogram of the AIC values of species interaction models with all possible groupings of interaction coefficients.
		The green line shows the AIC value (\icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}) of the ungrouped model, in which all competition coefficients are fitted independently.
		The red line shows the AIC value (\icnum{\Sexpr{brute_data$fully_grouped_statistics[[ic]]}}) of the fully grouped model, where every pair of species shares a single interaction coefficient.
	}
	\label{fig:aic}
\end{figure}

@@

Considering only models in which the rows and columns were grouped using the same grouping, the AIC values ranged from \icnum{\Sexpr{min(brute_data$equivalently_grouped_statistics[[ic]])}} to \icnum{\Sexpr{max(brute_data$equivalently_grouped_statistics[[ic]])}}; neither the best nor worst overall models had equivalently grouped rows and columns.
The total Akaike weight assigned to these models was \probnum{\Sexpr{brute_data$equivalently_grouped_weight}}; more than expected by chance (\probnum{\Sexpr{brute_data$equivalently_grouped_expected_weight}}), but not significantly so (Monte Carlo permutation test, $p=\probnum{\Sexpr{brute_data$equivalently_grouped_weight_p #$}}$).
This indicates that the most parsimonious model is not especially likely to be one that groups the rows and columns equivalently.
